%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}

\usepackage{draftwatermark}

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Andrew B. Maurer}{
%July 1, 1992
}{Last update on \today}

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Contact Info}
\vspace{-1.3em}
\begin{multicols}{2}
\noindent
Boyd Graduate Research Studies\\
Department of Mathematics\\
Athens, Georgia, 30602 \\
\texttt{http://andrewmaurer.github.io} \\
\texttt{andrew.b.maurer@gmail.com}
\end{multicols}
\blfootnote{Last Updated \today.}

\spacedhrule{0em}{-0.4em}

\roottitle{Summary}  % a root section title

\vspace{-1.3em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent \emph{Motivated and independent mathematician with broad interests in technical fields including data science, open source software, and science education.}
\\
\\
Trained as a mathematician, Andrew grasps abstract concepts quickly and is able to apply these concepts concretely to return results.

Andrew entered college in 2010 and blew through the undergraduate mathematics curriculum. Following a \emph{Research Experience for Undergraduates} after his sophomore year of college, Andrew completed the basic graduate sequences in mathematics. Supplemented by his computer science coursework, ---

\end{multicols}

\spacedhrule{0em}{-.04em}

\roottitle{Education}

\headedsection
  {University of Georgia}
  {\textsc{Athens, Georgia}} {%
  \headedsubsection
    {Mathematics, Ph.D Candidate}
    {2014 -- Present}
    {\bodytext{Advisor: Daniel K. Nakano. My research is on representation theory, with particular emphasis on the cohomology and support variety theory of Lie superalgebras. Additionally participated in research in tropical geometry and algebraic geometry, as well as projects in data science and statistics. Served as president and secretery for graduate student organization, logistic organizer for student algebraic geometry seminar, and logistic organizer for graduate visitation day.}}
}

\headedsection
  {University of Massachusetts}
  {\textsc{Amherst, Massachusetts}} {%
  \headedsubsection
    {Mathematics, Bachelor of Science. Computer Science, Minor.}
    {2010 -- 2014}
    {\bodytext{Advisor: Farshid Hajir. Exceptional amount of graduate coursework in analysis, algebra, geometry, and number theory. Multiple research projects in number theory and knot theory. Senior thesis elaborated on research paper by writing code to collect data concerning a family of polynomials which was in turn used to prove an original result.}}
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills}

\begin{itemize}
  \item \textbf{Software:} \textit{Operating Systems:} Windows, GNU/Linux, Mac OS. \textit{Scripting:} Bash, Perl. \textit{General Programming:} Python, Java. \textit{Mathematical Programming:} 
  \item \textbf{Teaching:}
  \item \textbf{Research:}
\end{itemize}


\spacedhrule{0.5em}{-0.4em}

\roottitle{Experience}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
